A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-23 main.tex
Updates from Overleaf
proof reading

% Keywords
\keyword{
Head and Neck Squamous Cell Carcinoma (HNSCC);
%Genome Database\sep
the Cancer Genome Atlas (TCGA);
RNA-sequencing;
Survival Analysis;
Optimal Cutoff;
%Biomarker\sep % Discovery\sep
%Tumor Type-agnostic Therapy\sep
%Immuno-Oncology\sep
%Targeted Therapy\sep
%Systemic Therapy\sep
%Surgical Margin
}

@@

%注意 強調GSE2837: 
%The prognostic significance of the candidate genes has been validated by an independent patient cohort.
% validation by GSE2837 cohort (with web-tools)
%\subsubsection*{GSE2837} % non-TCGA
% from Anwser2-2
%by GEO GSE2837 HNSCC dataset (PrognoScan)
After the discovery by our workflow, we validated the suggested 20 biomarkers in the other independent \acrshort{hnscc} cohort (GSE2837).
The survival significance (Kaplan-Meier \textit{P} value) is in the following probes of 10 genes:\\
1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
%17 out of 20 candidates
%?DKK1 (0.253635), 
%Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
Thus, these 10 out of 20 candidates have been confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort. Please see Kaplan-Meier plots in Supplementary Figure S1.%\ref{fig:fig_GSE2837}.

@@

\caption{ The 10 candidate genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted \textit{P} value) }

@@

\caption{The 10 candidate genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected \textit{P} value) }

@@

\subsection{Validation by Web-based Tools}
% GSE2837 validated candidates: 10
We also utilized another approach of web-based tools (TCGA) to analyze our candidates.
%\subsubsection*{SurvExpress} % TCGA
% 2021/01/23 pdf x 12 from SurvExpress
SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data. Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier \textit{P} value) shows in 6 genes:\\ % SurvExpress 有類似的結果:
1) poor prognosis: CAMK2N1 (0.000006), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008);\\
%, STIP1 (0.001), DKC1 (0.01);\\
%DKK1 (0.00005), CAMK2N1 (0.048214), STC2 (0.001), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
2) better prognosis: FCGBP (0.001).\\
%ZNF557 (0.0007), ZNF266 (0.00008), IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
%17 out of 20 candidates
%?DKK1 (0.253635),
The 6 out of 10 candidate genes are also confirmed by a comparative study using SurvExpress with the TCGA cohort. Please see Supplementary Figure S2.%\ref{fig:fig_SurvExpress}.
% moved to supplementary file: Supplementary_figures.tex
% \linksupplementary{Supplementary_figures.pdf},

% % SurvExpress 沒有類似的結果是因為:
%Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
Nevertheless, the survival prediction could not be found in FOXA2, IL19, IQCN, KIAA1683, or NPB using SurvExpress.
Our workflow has the advantage to find ai optimal cutpoint of that \acrshort{rna} expression data to maximize coverage during candidate mining.
%因為 cutoff 不適當，這也就是我們 pvalueTex \textit{P} 的設計目的與強項

%\subsubsection{HPA} %still TCGA's RNA-Seq
The Human Protein Atlas project (HPA) has proteomics analysis based on 26,941 antibodies targeting 17,165 unique proteins. The HPA's Pathology Atlas analyzes each protein in patients, using \acrshort{ihc} analysis based on tissue microarrays (TMAs) adopted from TCGA. Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
All transcriptomics data has been retrieved from the TCGA, and all proteomics data has been generated in-house using the same antibodies.
Our 5 candidates (e.g. CAMK2N1, PGK1, SURF4, USP10, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrfull{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19). 
FCGBP is on the list of favorable prognostic genes as well.
% DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, and DKC1
% ZNF557, ZNF266, and FCGBP
Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level (HPA database, available at https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+\\cancer)\cite{Ren2020}.
% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
%found at Human Protein Atlas dataset 
(Please see Supplementary Figure S3)%\ref{fig:fig_HPA_USP10})
% moved to Supplementary

@@

% PGK1
Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R). 
The resistance is associated with the up-regulated expression of PGK1, CD55, ATP-binding cassette transporter genes (e.g., MDR1, MRP1, and MRP2), and down-regulated expression Caveolin 1\cite{Nakamura2005}.
PGK1 is responsive in hypoxia status, since it is one of HIF-1\alpha regulated gene revealed in HNSCC\cite{Peng2011}\cite{Shih2017}.

@@

% second limitation:
%\subsubsection{Cancer type-agnostic study}
Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
% *** yes here
In our previous work, altered glucose metabolism (e.k.a. the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrlong{slc2a4} (\acrshort{slc2a4}, or \acrlong{glut4}, \acrshort{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}\cite{Mani2020}.
% Cited In for PMID: 28061796
Lactic acidosis induced \acrshort{glut4} overexpression was also found in lung cancer cells\cite{Prado-Garcia2020}. 
%The overexpression of \acrshort{glut4} will lead to higher glucose uptake in proliferating cancer cells\cite{Mani2020}.
%There is a trend toward cancer type-agnostic study. 
Currently, Pembrolizumab and nivolumab's success has been based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
It shows a model of tumor type-agnostic therapy\cite{Yan2018}.
%*** PD-L1/PD-L2 is a biomarker; Keynote-012
There are several common biomarkers of \acrfull{ici} under evaluation, including \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
The other \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019} (ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (NCT04080804) studies.

@@

@@

%discussion: the third limitation
There are eighty-one ($X_1 ... X_{81}$) physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, 
% since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features from holistic cancer care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status. (see Figure \ref{fig:figure5})
%
World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic, and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
Core principles can be taken to achieve people-centred and integrated health service delivery. 
The first principle is holistic – focusing on physical, socioeconomic, mental, and emotional well-being. 
Holistic care has been defined that care and sees the person as a whole with psychological, social, and environmental levels of needs and goals.
%that considers  factors rather than just the symptoms of disease or ill-health.
The second principle is empowering – supporting people to manage and take responsibility for their health,
%Empowerment: the process of supporting people and communities to take control of their own health needs resulting, 
for example, in the uptake of healthier behaviors or the ability to self-manage illnesses.
People-centred care requires that people have the education and support they need to make decisions and participate in their care.
%Glossary:
%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways. People-centred care also requires that people have the education and support they need to make decisions and participate in their own care. It is organized around the health needs and expectations of people rather than diseases (7,8) 
%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
%(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)

%*** make Figure 5 holistic: Figure_5_holisticCare.pdf
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{Figure_5_holisticCare.pdf}
\bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
{\\Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment will trigger emotional reception. The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion. The physical body's internal environment (cells) alters epigenetic control in gene regulation and mRNA expression. In a long incubation time, the tissue/cells will be transformed into dysplasia then malignancy with helping from known carcinogens.\\
Cancer care - Holistic care should take care of cancer patients' spiritual, emotional, physical, and socioeconomic needs. Physical care will be carried out by medication therapy or surgery. After establishing a therapeutic relationship, the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease.\\
Suggested healthcare record - Besides physical, pathological, or psychological data, electric healthcare records (EHR) and \acrshort{tcga} should collect "holistic features".}
\label{fig:figure5}
\end{figure}
%meridian and emotion has mutual reaction
%meridian effect tissue and organ
%(autonomic nerve system, myofascial network, prefrontal cortex)
%placebo-effect influence on drug discovery
%gene expression in deep learning
%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
%慈悲心 利他心
%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
%#正念 除了可以減壓，還可以治癒疼痛
% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症

@@

The Chinese Qigong and Tai Chi, belonging to movement-meditative-breathing interventions, also encourage mindfulness and self-awareness. 

@@

A systematic review of spiritually based interventions and psychoneuroimmunological outcomes in breast cancer survivorship was reported by Hulett et al.\cite{Hulett2016}. 

@@

Thus, cortisol is one of the most common (objective) outcomes studied in psychoneuroimmunological (PNI) factors. % others: interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV

@@

%%%% PCA and ECA: the way to delivery of MBSR
The therapeutic relationship is essential towards spiritual care.
According to clinical experience in healthcare, sometimes patients could tell the physicians: "How amazing it is. I want to talk about myself more when I visit this doctor whom I trust."
In 1979, Rogers wrote: "I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful."\cite{Rogers1979}
Carl Rogers developed person-centered theory that the therapist is providing the appropriate social-environmental conditions for their patients\cite{Rogers1957}\cite{Joseph2004}\cite{Griffiths2013}.
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}:\\
%For constructive personality change to occur, it is necessary that these conditions exist and continue over a period of time: 
1. Two persons are in psychological contact. \\
2. The first, whom we shall term the client, is in a state of incongruence (or not harmony), being vulnerable or anxious. \\
3. The second person, whom we shall term the therapist, is congruent
or integrated with the relationship. \\
4. The therapist experiences "unconditional positive regard" for the client. \\
5. The therapist experiences an empathic understanding of the client's
internal frame of reference and endeavors to communicate this experience to the client. \\
6. The communication to the client of the therapist's empathic understanding and unconditional positive regard is to a minimal degree achieved.\\
%empowering
%(一)雙方有心理的接觸。
%(二)當事人正感到焦慮或不一致(incongruence)。 
%(三)治療者在治療關係中是一致的 (congruence, agreement or harmony; compatibility)、真實的或真誠的。
%(四)治療者能夠對當事人表現出無條件的關懷。無條件關懷(不批判/頓悟)
%(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
%(六) 第五點只要有個適當的開始，療癒就會開始
%Dealing with negative emotions. 情緒影響，造成焦慮、發炎、免疫 Cancer
As the cancer patient feels intense negative emotions of extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, 
%七情: 喜、怒、思、悲、恐、驚、憂
depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is to stay with the patient’s experiences. 
% 只是陪伴
%The research implication is to investigate the necessity and sufficiency of the six conditions.
%Rogers, C. R. A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework. in Psychology: A Study of a Science. Study 1, Volume 3: Formulations of the Person and the Social Context (ed. Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}
%PCA理論 by *** Tex Chi
%治療關係的六核心條件: 說好話 眼對眼 engaging 用真心
%以心印心 engaging
%身心相連 body-mind connection
%捨末求本 find the source: emotion
Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases. They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner. (see Figure \ref{fig:figure5})
%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
%「把自己當藥方開出去」
%Spirituality
%慈悲心 compassion 
%同情心 sympathy
%同理心 empathy
%non-verbal contact

@@

Epigenetics control says that genetic expression is directly due to the environment of our cells and our perception of the environment\cite{Gustafson2017}. (see Figure \ref{fig:figure5})

@@

Some studies showed that after 8 hours of meditation, the expression of some inflammatory genes changed\cite{Gustafson2017}.

@@

Warburg effect\cite{Warburg1956}\cite{Chang2017b} is an example of carcinogenesis, metabolic reprogramming cells by some environmental factors.

@@

Being subconscious, those programs acquired from other people before age 7, are occurring without conscious recognition and awareness. 

@@

Genes are not self-actualizing. 

@@

Over 90\% of disease is a total reflection of the environment and especially our programming.

@@

The mind-brain-body axis shows that subconscious fear causes releasing of inflammatory and stress hormones from the brain in terms of cell alteration in DNA methylation, mutation, mRNA expression. Carcinogenesis will occur if the reprogramming is persistent for a longer time. (see Figure \ref{fig:figure5})

@@

and cancer initiation\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}. %HNSCC

>>>>

% Keywords
\keyword{
Head and Neck Squamous Cell Carcinoma (HNSCC);
%Genome Database\sep
the Cancer Genome Atlas (TCGA);
RNA-sequencing;
Survival Analysis;
Optimal Cutoff;
%Biomarker\sep % Discovery\sep
%Tumor Type-agnostic Therapy\sep
%Immuno-Oncology\sep
%Targeted Therapy\sep
%Systemic Therapy\sep
%Surgical Margin
Holistic Cancer Care;
Therapeutic Relationship
}

@@

%注意 強調GSE2837: 
%The prognostic significance of the candidate genes has been validated by an independent patient cohort.
% validation by GSE2837 cohort (with web-tools)
%\subsubsection*{GSE2837} % non-TCGA
% from Anwser2-2
%by GEO GSE2837 HNSCC dataset (PrognoScan)
After the discovery by our workflow, we validated the those 20 genes in the other independent \acrshort{hnscc} cohort (GSE2837).
The survival significance (Kaplan-Meier \textit{P} value) is in the following probes among 10 genes:\\
1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587);\\ % FOXA2 (0.038125)
2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);\\
%17 out of 20 candidates
%?DKK1 (0.253635), 
%Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
Thus, these 10 candidates have been confirmed by a comparative study using the GSE2837 dataset other than the TCGA cohort. Please see Kaplan-Meier plots in Supplementary Figure S1.%\ref{fig:fig_GSE2837}.

@@

\caption{ The top 10 genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted \textit{P} value) }

@@

\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected \textit{P} value) }

@@

\subsection{Validation by Web-based Tools}
% GSE2837 validated candidates: 10
We also utilized another approach of web-based tools (TCGA) to analyze our candidates.
%\subsubsection*{SurvExpress} % TCGA
% 2021/01/23 pdf x 12 from SurvExpress
SurvExpress\cite{Aguirre-Gamboa2013} is one of the web-based tools for Biomarker comparison and validation of survival gene expression data. Using their TCGA HNSCC cohort (June 2016, n=502), the survival significance (Kaplan Meier \textit{P} value) shows in 6 genes:\\ % SurvExpress 有類似的結果:
1) poor prognosis: CAMK2N1 (0.000006), PGK1 (0.01), SURF4 (0.002), USP10 (0.002), NDFIP1 (0.000008);\\
%, STIP1 (0.001), DKC1 (0.01);\\
%DKK1 (0.00005), CAMK2N1 (0.048214), STC2 (0.001), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
2) better prognosis: FCGBP (0.001).\\
%ZNF557 (0.0007), ZNF266 (0.00008), IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
%17 out of 20 candidates
%?DKK1 (0.253635),
The 6 out of 10 candidate genes are also confirmed by a comparative study using SurvExpress with the TCGA cohort. Please see Supplementary Figure S2.%\ref{fig:fig_SurvExpress}.
% moved to supplementary file: Supplementary_figures.tex
% \linksupplementary{Supplementary_figures.pdf},
% % SurvExpress 沒有類似的結果是因為:
%Nevertheless, the survival prediction could not be found in FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB using SurvExpress. 
Nevertheless, the survival prediction could not be found in FOXA2, IL19, IQCN, KIAA1683, or NPB using SurvExpress.
Our workflow has the advantage to find an optimal cutpoint of that \acrshort{rna} expression data to maximize coverage during candidate mining.
%因為 cutoff 不適當，這也就是我們 pvalueTex \textit{P} 的設計目的與強項

%\subsubsection{HPA} %still TCGA's RNA-Seq
The Human Protein Atlas project (HPA) has proteomics analysis based on 26,941 antibodies targeting 17,165 unique proteins. The HPA's Pathology Atlas analyzes each protein in patients, using \acrshort{ihc} analysis based on tissue microarrays (TMAs) adopted from TCGA. Kaplan-Meier survival analyses are based on RNA-Seq expression levels of human genes in HNSCC tissue and the clinical outcome.
All transcriptomics data has been retrieved from the TCGA, and all proteomics data has been generated in-house using the same antibodies.
Our 5 candidates (e.g. CAMK2N1, PGK1, SURF4, USP10, and NDFIP1) are also on the list of unfavorable prognostic genes for HNSCC from \acrshort{hpa} (available at https://www.proteinatlas.org/humanproteome/pathology/head+and+neck+cancer, Version: 20.0 updated: 2020-11-19). 
FCGBP is on the list of favorable prognostic genes as well.
% DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, and DKC1
% ZNF557, ZNF266, and FCGBP
Moreover, overexpression of ubiquitin-specific peptidase 10 (USP10), one of the autophagy-related genes, has a poor prognostic impact on HNSCC, which has been proved at mRNA and protein level (HPA database, available at https://www.proteinatlas.\\
org/ENSG00000103194-USP10/pathology/head+and+neck+cancer)\cite{Ren2020}.
% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
%found at Human Protein Atlas dataset 
(Please see Supplementary Figure S3)%\ref{fig:fig_HPA_USP10})
% moved to Supplementary

@@

% PGK1
Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R). 
The resistance is associated with the up-regulated expression of PGK1, CD55, ATP-binding cassette transporter genes (e.g., MDR1, MRP1, and MRP2), and down-regulated expression Caveolin 1\cite{Nakamura2005}.
PGK1 is responsive in hypoxia status, since it is one of \acrshort{hif}-1 alpha regulated gene revealed in HNSCC\cite{Peng2011}\cite{Shih2017}.

@@

@@

%\subsubsection{Tumor-agnostic Research}
% second limitation:
\subsubsection{Cancer Type-agnostic Study}
Our strategy still has the strength to explore the more possible biomarkers from \acrshort{rnaseq} datasets in cancer research.
% *** yes here
In our previous work, altered glucose metabolism (e.k.a. the Warburg effect\cite{Warburg1956}) promotes the progression of \acrshort{hnscc}, which is partially attributed to the \acrlong{slc2a4} (\acrshort{slc2a4}, or \acrlong{glut4}, \acrshort{glut4}) and \acrfull{trim24} pathway\cite{Chang2017b}\cite{Mani2020}.
% Cited In for PMID: 28061796
Lactic acidosis induced \acrshort{glut4} overexpression was also found in lung cancer cells\cite{Prado-Garcia2020}. 
%The overexpression of \acrshort{glut4} will lead to higher glucose uptake in proliferating cancer cells\cite{Mani2020}.
%There is a trend toward cancer type-agnostic study. 
Currently, Pembrolizumab and nivolumab's success has been based on a common biomarker (e.g., \acrshort{pd1}) crossing several types of cancer.
It shows a model of tumor type-agnostic therapy\cite{Yan2018}.
%*** PD-L1/PD-L2 is a biomarker; Keynote-012
There are several common biomarkers of \acrfull{ici} under evaluation, including \acrfull{til}, \acrfull{ifng}, and \acrfull{tmb}\cite{Gavrielatou2020}.
The other \acrshort{ici}, anti-\acrshort{lag3} (pelatlimab), is currently evaluated under the phase I/IIA\cite{Cristina2019} (ClinicalTrials.gov Identifier: NCT01968109) and II-IVA\cite{Neal2019} (NCT04080804) studies.

@@

%discussion: the third limitation
There are eighty-one ($X_1 ... X_{81}$) physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, 
% since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features from holistic cancer care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status (see Figure \ref{fig:figure5}).

%
World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic, and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
Core principles can be taken to achieve people-centred and integrated health service delivery. 
The first principle is holistic – focusing on physical, socioeconomic, mental, and emotional well-being. 
Holistic care has been defined that care and sees the person as a whole with psychological, social, and environmental levels of needs and goals.
%that considers  factors rather than just the symptoms of disease or ill-health.
The second principle is empowering – supporting people to manage and take responsibility for their health,
%Empowerment: the process of supporting people and communities to take control of their own health needs resulting, 
for example, in the uptake of healthier behaviors or the ability to self-manage illnesses.
People-centred care requires that people have the education and support they need to make decisions and participate in their care.
%Glossary:
%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways. People-centred care also requires that people have the education and support they need to make decisions and participate in their own care. It is organized around the health needs and expectations of people rather than diseases (7,8) 
%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
%(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)

%*** make Figure 5 holistic: Figure_5_holisticCare.pdf
\begin{figure}[hp]
\centering
\includegraphics[width=14cm]{Figure_5_holisticCare.pdf}
\bcaption{The concept of holistic care for \acrshort{hnscc} patients.}
{\\Beyond carcinogenesis - Under the mind-brain-body axis, a stressful environment (giant \textcolor{black}{black} arrow) will trigger emotional reception. The subconscious mind (brain) will release stress hormones and inflammation signals in response to the emotion. The physical body's internal environment (cells) alters epigenetic control in gene regulation and mRNA expression. In a long incubation time, the tissue/cells will be transformed into dysplasia then malignancy (e.x. HNSCC) with helping from known carcinogens.\\
Cancer care - Holistic care should take care of cancer patients' spiritual, emotional, physical, and socioeconomic needs. Physical care will be carried out by medication therapy or surgery. After establishing a therapeutic relationship (TR), the physicians' spiritual properties (empathy, sympathy, and compassion) will engage their patients and recover their self-compassion to gain resilience against the disease through their mind-brain-body axis.
Thus, we suggest electric healthcare records (EHR) include physical, pathological, psychological data, and even more spiritual information. The \acrshort{tcga} should collect "holistic features" as well (\textcolor{green}{green} dashed line).}
\label{fig:figure5}
\end{figure}
%meridian and emotion has mutual reaction
%meridian effect tissue and organ
%(autonomic nerve system, myofascial network, prefrontal cortex)
%placebo-effect influence on drug discovery
%gene expression in deep learning
%Ching, T. et al. Opportunities and obstacles for deep learning in biology and medicine. J. R. Soc. Interface 15, (2018).
%慈悲心 利他心
%博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的
%#正念 除了可以減壓，還可以治癒疼痛
% modify the dark environment 改造患者的心，就能改造他的身體環境，有利消除癌症

@@

The Chinese Qigong and Tai Chi, belonging to movement-meditative-breathing interventions, also encourage (dynamic) mindfulness and self-awareness. 

@@

A systematic review of spiritually based interventions and psychoneuroimmunological (PNI) outcomes in breast cancer survivorship was reported by Hulett et al.\cite{Hulett2016}. 

@@

Thus, cortisol is one of the most common (objective) outcomes studied in PNI factors. % others: interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV

@@

%%%% PCA and ECA: the way to delivery of MBSR
The therapeutic relationship (TR) is essential towards spiritual care.
According to clinical experience in healthcare, sometimes patients could tell the physicians: "How amazing it is. I want to talk about myself more when I visit this doctor whom I trust."
In 1979, Carl Rogers wrote\cite{Rogers1979}: "I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful."
Carl Rogers developed person-centered theory that the therapist is providing the appropriate social-environmental conditions for their patients\cite{Rogers1957}\cite{Joseph2004}\cite{Griffiths2013}.
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers in 1957\cite{Rogers1957}:\\
%For constructive personality change to occur, it is necessary that these conditions exist and continue over a period of time: 
1. Two persons are in psychological contact. \\
2. The first, whom we shall term the client, is in a state of incongruence (or not harmony), being vulnerable or anxious. \\
3. The second person, whom we shall term the therapist, is congruent
or integrated with the relationship. \\
4. The therapist experiences "unconditional positive regard" for the client. \\
5. The therapist experiences an empathic understanding of the client's
internal frame of reference and endeavors to communicate this experience to the client. \\
6. The communication to the client of the therapist's empathic understanding and unconditional positive regard is to a minimal degree achieved.\\
%empowering
%(一)雙方有心理的接觸。
%(二)當事人正感到焦慮或不一致(incongruence)。 
%(三)治療者在治療關係中是一致的 (congruence, agreement or harmony; compatibility)、真實的或真誠的。
%(四)治療者能夠對當事人表現出無條件的關懷。無條件關懷(不批判/頓悟)
%(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
%(六) 第五點只要有個適當的開始，療癒就會開始
%Dealing with negative emotions. 情緒影響，造成焦慮、發炎、免疫 Cancer
As the cancer patient feels intense negative emotions of extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, 
%七情: 喜、怒、思、悲、恐、驚、憂
depression, fatigue, stress, it is not the patient-centred therapist’s task to remove these feelings: the task is to stay with the patient’s experiences. 
% 只是陪伴
%The research implication is to investigate the necessity and sufficiency of the six conditions.
%Rogers, C. R. A Theory of Therapy, Personality, and Interpersonal Relationships: As Developed in the Client-centered Framework. in Psychology: A Study of a Science. Study 1, Volume 3: Formulations of the Person and the Social Context (ed. Koch, S.) 184–256 (McGraw Hill, 1959).\cite{Rogers1959}
%PCA理論 by *** Tex Chi
%治療關係的六核心條件: 說好話 眼對眼 engaging 用真心
%以心印心 engaging
%身心相連 body-mind connection
%捨末求本 find the source: emotion
Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion is induced by the suffering of patients from those diseases. They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure \ref{fig:figure5}).
%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
%「把自己當藥方開出去」
%Spirituality
%慈悲心 compassion 
%同情心 sympathy
%同理心 empathy
%non-verbal contact

@@

Epigenetics control says that genetic expression is directly due to the environment of our cells and our perception of the environment\cite{Gustafson2017} (e.x. stressful environment, see Figure \ref{fig:figure5}).

@@

Study showed that after several hours of meditation, the expression of some inflammatory genes changed\cite{Gustafson2017}.

@@

Warburg effect\cite{Warburg1956}\cite{Chang2017b} is an example of carcinogenesis and metabolic reprogramming of cells by some environmental factors.

@@

%Being subconscious, those programs acquired from other people before age 7, are occurring without conscious recognition and awareness. 

@@

@@

Over 90\% of disease is a total reflection of the environment.% and especially our programming.

@@

The mind-brain-body axis shows that subconscious fear causes releasing of inflammatory and stress hormones from the brain in terms of cell alteration in DNA methylation, mutation, mRNA expression. 
%Carcinogenesis will occur if the reprogramming is persistent for a longer time.

@@

and cancer initiation\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}.(see Figure \ref{fig:figure5}) %HNSCC
